---
title: "K-means Clustering with adjusted script"
author: "Amy van der Ham"
date: "12/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Try out k-means clustering on the existing GloVe embedding on which the final filter is applied.

```{r}
# load libraries
library(dplyr)
library(cluster)
library(ggplot2)
library(devtools)
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
```

# set.seed prior to running the k-means clustering 
```{r}
set.seed(88)
```

## Load the embeddings 
```{r}
# load glove word embedding file
glove_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_final.RData")

str(glove_embedding)

# load glove bigrams word embedding file
glove_bigrams_embedding <-  readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_bigrams.RData")

str(glove_bigrams_embedding)

# load w2v word embedding file
w2v_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding.RData")

str(w2v_embedding)

# load w2v bigrams word embedding file
w2v_bigrams_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_bigrams_embedding.RData")

str(w2v_bigrams_embedding)
```

# Look at wich words are close to health
```{r}
library(text2vec)
# create function to find similar words based on cosine distance
find_similar_words <- function(word, embedding_matrix, n = 5) {
  similarities <- embedding_matrix[word, , drop = FALSE] %>%
    sim2(embedding_matrix, y = ., method = "cosine")
  
  similarities[, 1] %>% sort(decreasing = TRUE) %>% head(n)
}

# Run function on the word health and see the 25 closest words based on cosine similarity. Compare the different embeddings.
find_similar_words("white",glove_embedding,50)
find_similar_words("white",w2v_embedding,50)
find_similar_words("white",w2v_bigrams_embedding,50)
find_similar_words("mental_health",w2v_bigrams_embedding,50)

# check if socio-emotional and socioemotional are similar words in the glove bigrams embedding
find_similar_words("socio-emotional",glove_bigrams_embedding,25)
find_similar_words("socioemotional",glove_bigrams_embedding,25)
```

# Clustering analysis
Run kmeans with a value for k of 75, 100, 125, 150 and compare the results. Run this for each embedding  
```{r}
# fit the k-means clustering with 75 clusters, glove
kmeans_fit75 <- kmeans(glove_embedding, 75, iter.max = 30, nstart = 25)

# fit the k-means clustering with 100 clusters
kmeans_fit100 <- kmeans(glove_embedding, 100, iter.max = 30, nstart = 25)

# fit the k-means clustering with 125 clusters
kmeans_fit125 <- kmeans(glove_embedding, 125, iter.max = 30, nstart = 25)

# fit the k-means clustering with 150 clusters
kmeans_fit150 <- kmeans(glove_embedding, 150, iter.max = 30, nstart = 25)
```

# Look at the fit. 
```{r}

# fit the k-means clustering with 75 clusters, w2v
kmeans_fit75_w2v <- kmeans(w2v_embedding, 75, iter.max = 30, nstart = 25)

# fit the k-means clustering with 75 clusters, w2v bigrams
kmeans_fit75_bigr <- kmeans(w2v_bigrams_embedding, 75, iter.max = 30, nstart = 25)
# results 
kmeans_fit75
# 25.2%
kmeans_fit75_w2v
# 20.2%
kmeans_fit75_bigr
# 20.3% of the total variance in the data set that is explained by the clustering

# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster75 <- as.data.frame(cbind(row.names(glove_embedding), kmeans_fit75$cluster))
# add column names
names(words_with_cluster75) <- c("word", "kmeans75")

# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster75_w2v <- as.data.frame(cbind(row.names(w2v_embedding), kmeans_fit75_w2v$cluster))
# add column names
names(words_with_cluster75_w2v) <- c("word", "kmeans75")


# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster75_w2v_bigr <- as.data.frame(cbind(row.names(w2v_bigrams_embedding), kmeans_fit75_bigr$cluster))
# add column names
names(words_with_cluster75_w2v_bigr) <- c("word", "kmeans75")

# Mental
# find out in which cluster the word mother is assigned
words_with_cluster75[words_with_cluster75$word == "mental", ]
words_with_cluster75_w2v[words_with_cluster75_w2v$word == "mental", ]
words_with_cluster75_w2v_bigr[words_with_cluster75_w2v_bigr$word == "mental", ]

cluster_mental_glv <- subset(words_with_cluster75, subset=kmeans75 == 9)

cluster_mental_w2v <- subset(words_with_cluster75_w2v, subset=kmeans75 == 8)

cluster_mental_w2v_bigr <- subset(words_with_cluster75_w2v_bigr, subset=kmeans75 == 34)

# find out in which cluster the word mother is assigned
words_with_cluster75[words_with_cluster75$word == "mother", ]
words_with_cluster75_w2v[words_with_cluster75_w2v$word == "mother", ]
words_with_cluster75_w2v_bigr[words_with_cluster75_w2v_bigr$word == "mother", ]

cluster_mother_glv <- subset(words_with_cluster75, subset=kmeans75 == 74)

cluster_mother_w2v <- subset(words_with_cluster75_w2v, subset=kmeans75 == 19)

cluster_mother_w2v_bigr <- subset(words_with_cluster75_w2v_bigr, subset=kmeans75 == 43)
```

# Assign cluster number to data frame and create (sub) data frame for each cluster. See if I can make some functions for this as I repeat this piece of code quite often. 
```{r}
# create function for making a data frame that contains a column with information on the cluster assignment. 
create_df_with_clst_assignment <- function(embedding, kmeans_fit) {
  # Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster <- as.data.frame(cbind(row.names(embedding), kmeans_fit$cluster))
# add column names
names(words_with_cluster) <- c("word", "kmeans100")
return(words_with_cluster)
}

# dit heeft denk geen zin zit ik ook te kutten met de naam. 

# create function for making a separate data frame containing the words that belong to one specific cluster
create_cluster_df <- function(df_with_cluster_assignment, cluster_to_subset) {
  df_with_cluster_assignment[df_with_cluster_assignment[,2] == 1, ]
}


create_cluster_df(words_with_cluster, 89)




# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster <- as.data.frame(cbind(row.names(glove_embedding), kmeans_fit75$cluster))
# add column names
names(words_with_cluster) <- c("word", "kmeans100")

# make a df for the first 5 cluster results, quickly "eyeball" results
cluster1 <- subset(words_with_cluster, subset=kmeans100 == 1)
cluster2 <- subset(words_with_cluster, subset=kmeans100 == 2)
cluster3 <- subset(words_with_cluster, subset=kmeans100 == 3)
cluster4 <- subset(words_with_cluster, subset=kmeans100 == 4)
cluster5 <- subset(words_with_cluster, subset=kmeans100 == 5)

# Mother 
# find out in which cluster the word mother is assigned
words_with_cluster[words_with_cluster$word == "mother", ]

# make a df of cluster 91
cluster91 <- subset(words_with_cluster, subset = kmeans100 == 91)

# Health
# find out in which cluster the word health is assigned
words_with_cluster[words_with_cluster$word == "health", ]

# make a df of cluster 46
cluster46 <- subset(words_with_cluster, subset=kmeans100 == 46)

# Environment
# find out in which cluster the word environment is assigned
words_with_cluster[words_with_cluster$word == "environment", ]

# make a df of cluster 82
cluster82 <- subset(words_with_cluster, subset=kmeans100 == 82)

# Depression
# find out to which cluster the word depression is assigned so that I can check if all the forms of depression are in there. 
words_with_cluster[words_with_cluster$word == "depression", ]

# make a df of cluster 6
cluster6 <- subset(words_with_cluster, subset=kmeans100 == 6)
 
words_with_cluster[words_with_cluster$word == "depressed", ]
words_with_cluster[words_with_cluster$word == "depressive", ]
words_with_cluster[words_with_cluster$word == "nondepressed", ]
words_with_cluster[words_with_cluster$word == "antidepressant", ]

# kelly
# find out in which cluster the word Kelly is assigned so that I can check if all names are put together for example. 
words_with_cluster[words_with_cluster$word == "kelly", ]

# make a df of cluster 24
cluster24 <- subset(words_with_cluster, subset=kmeans100 == 24)

# cortisol
# find out in which cluster the word cortisol is assigned 
words_with_cluster[words_with_cluster$word == "cortisol", ]

# make a df of cluster 60
cluster60 <- subset(words_with_cluster, subset=kmeans100 == 60)

# empathy
# find out in which cluster the word empathy is assigned 
words_with_cluster[words_with_cluster$word == "empathy", ]

# make a df of cluster 38
cluster38 <- subset(words_with_cluster, subset = kmeans100 == 38)

# check the smallest cluster
cluster75 <- subset(words_with_cluster, subset = kmeans100 == 75)
# -> looks like this cluster represents related to India and Indian languages?  

# check the largest cluster
cluster61 <- subset(words_with_cluster, subset = kmeans100 == 61)
# -> mostly abbreviations. 

# check another large cluster 
cluster89 <- subset(words_with_cluster, subset = kmeans100 == 89)

# check another large cluster 
cluster94 <- subset(words_with_cluster, subset = kmeans100 == 94)
# -> again mostly abbreviations.

# check another small cluster 
cluster3 <- subset(words_with_cluster, subset = kmeans100 == 3)
# -> words that compare things such as easier, fewer, stronger etc. comparative adjective. 

cluster31 <- subset(words_with_cluster, subset = kmeans100 == 31)

# check to which cluster ethnicity belongs
words_with_cluster[words_with_cluster$word == "ethnicity", ]

# create df of cluster 14
cluster14 <- subset(words_with_cluster, subset = kmeans100 == 14)
```

# Some visualization try outs
```{r}
k_means_fit$centers
plot(glove_embedding, col = k_means_fit$cluster == 1)
points(k_means_fit$center == 2,)

test <- subset(k_means_fit, words_with_cluster$cluster == 1)

# try to add cluster assignment to glove_embedding
glove_emb_clst <- as.data.frame(glove_embedding)

cluster_assignment <- as.data.frame(cbind(row.names(glove_embedding), k_means_fit$cluster))

# add cluster assignment to dataframe with word vectors
glove_emb_clst$cluster <- cluster_assignment$V2

embedding_cluster


# create plot of separate cluster with tsne
library(Rtsne)
embedding_cluster91 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster91$word)

tsne <- Rtsne(embedding_cluster91, dims = 2, perplexity = 25, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster91_plot <- as.data.frame(embedding_cluster91)

embedding_cluster91_plot$word <- rownames(embedding_cluster91_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne$Y) %>%
  mutate(
    word = embedding_cluster91_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 91") +
  theme(legend.position = "none") +
  theme_minimal()
p


# try to create plot with PCA
# Dimension reduction using PCA
res_pca <- prcomp(glove_embedding,  scale = FALSE)
# Coordinates of individuals
ind_coord <- as.data.frame(get_pca_ind(res_pca)$coord)
# Add clusters obtained using the K-means algorithm
ind_coord$cluster <- factor(k_means_fit$cluster)
# Add Species groups from the original data sett
ind_coord$word <- rownames(glove_embedding)

eigenvalue <- round(get_eigenvalue(res_pca), 1)
variance_percent <- eigenvalue$variance.percent

# subset cluster 91 
ind_coord_clst91 <- ind_coord[ which(ind_coord$cluster == 91), ]


# create plot
library(ggpubr)

ggscatter(
  ind_coord_clst91, x = "Dim.1", y = "Dim.2", 
  label = "word", ellipse = FALSE, ellipse.type = "euclid", legend = "none",
  ggtheme = theme_minimal(),
  xlab = paste0("Dim 1 (", variance_percent[1], "% )" ),
  ylab = paste0("Dim 2 (", variance_percent[2], "% )" )
) 
```
Using PCA to create plot the position of the different words in the plot seem to make less sense to me than when using t-SNE. 

# TSNE of cluster 14 
```{r}
# create plot of separate cluster with tsne
embedding_cluster14 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster14$word)

tsne_14 <- Rtsne(embedding_cluster14, dims = 2, perplexity = 20, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster14_plot <- as.data.frame(embedding_cluster14)

embedding_cluster14_plot$word <- rownames(embedding_cluster14_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_14$Y) %>%
  mutate(
    word = embedding_cluster14_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 14") +
  theme(legend.position = "none") +
  theme_minimal()
p
```

# TSNE of cluster 31
```{r}
# create plot of separate cluster with tsne
embedding_cluster31 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster31$word)

tsne_31 <- Rtsne(embedding_cluster31, dims = 2, perplexity = 18, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster31_plot <- as.data.frame(embedding_cluster31)

embedding_cluster31_plot$word <- rownames(embedding_cluster31_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_31$Y) %>%
  mutate(
    word = embedding_cluster31_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 31") +
  theme(legend.position = "none") +
  theme_minimal() +
  xlim(-28, 25)
p
```

## Apply cluster analysis within a cluster (cluster 46) ##
```{r}
# create new subset data frame
embedding_cluster46 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster46$word)

# fit k-means
k_means_fit3_cluster46 <- kmeans(embedding_cluster46, 3, iter.max = 30, nstart = 25)

# look at the results
# look at the size of the clusters
k_means_fit3_cluster46$size
k_means_fit3_cluster46

# Create data frame in which the merge cluster assignment back to rows/word. 
words_with_cluster46_3 <- as.data.frame(cbind(row.names(embedding_cluster46), k_means_fit3_cluster46$cluster))
# add column names
names(words_with_cluster46_3) <- c("word", "kmeans3")

# make a df for the 3 cluster results
cluster46_1 <- subset(words_with_cluster46_3, subset=kmeans3 == 1)
cluster46_2 <- subset(words_with_cluster46_3, subset=kmeans3 == 2)
cluster46_3 <- subset(words_with_cluster46_3, subset=kmeans3 == 3)

# load library for visualization
library(factoextra)

# set max overlap to Inf to show all the labels in the plot. This does however make the plot unreadable
#options(ggrepel.max.overlaps = Inf)

# visualize the k-means (with k = 3) clusters
fviz_cluster(k_means_fit3_cluster46, data = embedding_cluster46,
palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07"),
ellipse.type = "euclid", # Concentration ellipse
star.plot = TRUE, # Add segments from centroids to items
repel = TRUE, # Avoid label overplotting (slow)
ggtheme = theme_minimal()
)

##  DETERMINING THE VALUE OF K
library(factoextra)
# Elbow method
fviz_nbclust(embedding_cluster46, kmeans, iter.max = 30, nstart = 25, method = "wss", k.max = 15) + geom_vline(xintercept = 11, linetype = 2) + # add line for better visualisation. 
  labs(subtitle = "Elbow method") # add subtitle
# -> not sure I interpret it correctly but would say the knee is at 6, 10 or 11?   
 
# Silhouette method
fviz_nbclust(embedding_cluster46, kmeans, iter.max = 30, nstart = 25, method = "silhouette", k.max = 15) +
  labs(subtitle = "Silhouette method")
# -> suggests setting k to 11 clusters

# Note that I have set nboot really low for obtaining a quick result.  
# Gap statistic
fviz_nbclust(embedding_cluster46, kmeans,
  iter.max = 30,
  nstart = 25,
  method = "gap_stat",
  k.max = 15,
  nboot = 5 # reduce it for lower computation time (but less precise results)
) +
  labs(subtitle = "Gap statistic method")
# -> suggests 1 cluster and second best option is 10. 

# try to determine number of cluster with NbClust package
library(NbClust)
nbclust_out <- NbClust(
  data = embedding_cluster46,
  distance = "euclidean",
  min.nc = 2, # minimum number of clusters
  max.nc = 15, # maximum number of clusters
  method = "kmeans", # one of: "ward.D", "ward.D2", "single", "complete", "average", "mcquitty", "median", "centroid", "kmeans"
  index = "silhouette"
)

nbclust_out
# -> this gives a different result than the shiloutte plot. I wonder what the reason for this is. 

# Another package for determine number of clusters
library(ClusterR) 

Optimal_Clusters_KMeans(embedding_cluster46, 
              max_clusters = 15, 
              criterion = "distortion_fK",
              fK_threshold = 0.85, 
              num_init = 3, 
              max_iters = 50,
              initializer = "kmeans++",
              tol = 1e-04, 
              plot_clusters = TRUE,
              verbose = T, 
              tol_optimal_init = 0.3, 
              seed = 1)
# -> do not really know how to interpret this. 

Optimal_Clusters_KMeans(embedding_cluster46, max_clusters = 15, plot_clusters = T, criterion = 'silhouette')
# -> 

# RUN ANALYSIS WITH 10 CLUSTERS
# fit kmeans with 10 clusters
k_means_fit10_cluster46 <- kmeans(embedding_cluster46, 10, iter.max = 30, nstart = 25)

library(cluster)
sil <- silhouette(k_means_fit10_cluster46$cluster, dist(embedding_cluster46))
fviz_silhouette(sil)
# -> the average silhouette width is low and there are quite some negative values. 

# # Create data frame in which the cluster assignment is merged back to rows/words.
words_with_cluster46_10 <- as.data.frame(cbind(row.names(embedding_cluster46), k_means_fit10_cluster46$cluster))
# add column names
names(words_with_cluster46_10) <- c("word", "kmeans10")

# cluster with highest silhouette value
cluster3_highestsil <- subset(words_with_cluster46_10, subset = kmeans10 == 3)

# cluster with second highest silhouette value
cluster7_2nd_highestsil <- subset(words_with_cluster46_10, subset = kmeans10 == 7) 

library(RColorBrewer)

# visualize the k-means (with k = 10) clusters
fviz_cluster(k_means_fit10_cluster46, data = embedding_cluster46,
palette = "Spectral",
ellipse.type = "euclid", # Concentration ellipse
star.plot = TRUE, # Add segments from centroids to items
repel = TRUE, # Avoid label overplotting (slow)
ggtheme = theme_minimal()
)
```

## Apply cluster analysis within a cluster (cluster 37) ##
The resulting clusters do not really make sense to me. 
```{r}
# create new subset data frame
embedding_cluster37 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster37$word)

# Silhouette method for determining k
fviz_nbclust(embedding_cluster37, kmeans, method = "silhouette") +
  labs(subtitle = "Silhouette method")
# -> suggests 2 or 5 as value for k

# fit k-means
k_means_fit5_cluster37 <- kmeans(embedding_cluster37, 5, iter.max = 30, nstart = 25)

# look at the size of the clusters
k_means_fit5_cluster37$size

# look at the results
k_means_fit5_cluster37 

# Create data frame in which the merge cluster assignment back to rows/word. 
words_with_cluster37_5 <- as.data.frame(cbind(row.names(embedding_cluster37), k_means_fit5_cluster37$cluster))
# add column names
names(words_with_cluster37_5 ) <- c("word", "kmeans5")

# make a df for the first 3 clusters
cluster37_1 <- subset(words_with_cluster37_5, subset=kmeans5 == 1)
cluster37_2 <- subset(words_with_cluster37_5, subset=kmeans5 == 2)
cluster37_3 <- subset(words_with_cluster37_5, subset=kmeans5 == 3)

# visualize the k-means (with k = 3) clusters
fviz_cluster(k_means_fit5_cluster37, data = embedding_cluster37,
palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07", "#8F00FF"),
ellipse.type = "euclid", # Concentration ellipse
star.plot = TRUE, # Add segments from centroids to items
repel = TRUE, # Avoid label overplotting (slow)
ggtheme = theme_minimal()
)
```


##CLUSTER ANALYSIS DETERMINING THE NUMBER OF CLUSTER FOR FULL DATASET##
# Determining the value of the parameter K for the glove_embedding matrix
```{r}
wssplot <- function(data, nc=15, seed=1234){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kmeans(data, centers=i, iter.max = 30)$withinss)}
  plot(1:nc, wss, type="b", xlab="Number of Clusters",
       ylab="Within groups sum of squares")}

wssplot(glove_embedding, nc=150)
```

-> looks like the elbow is at 20-24? We see a small increase in wss at k = 140.
# set seed again
```{r}
set.seed(88)
```

# Using the package factoextra
https://statsandr.com/blog/clustering-analysis-k-means-and-hierarchical-clustering-by-hand-and-in-r/#silhouette-method
```{r}
# Elbow method
fviz_nbclust(glove_embedding, kmeans, iter.max = 30, method = "wss", k.max = 150) + labs(subtitle = "Elbow method") # add subtitle

# geom_vline(xintercept = 4, linetype = 2) + # add line for better visualisation. I do not see a clear knee location in the plot. 

# Silhouette method
fviz_nbclust(glove_embedding, kmeans, iter.max = 50, nstart = 25, method = "silhouette", k.max = 150) +
  labs(subtitle = "Silhouette method")

# Takes to long so did not run this. Could turn nboot down. 
# Gap statistic
fviz_nbclust(glove_embedding, kmeans,
  nstart = 25,
  method = "gap_stat",
  nboot = 500 # reduce it for lower computation time (but less precise results)
) +
  labs(subtitle = "Gap statistic method")


# try to determine number of cluster with NbClust package
library(NbClust)
nbclust_out <- NbClust(
  data = glove_embedding,
  distance = "euclidean",
  min.nc = 2, # minimum number of clusters
  max.nc = 150, # maximum number of clusters
  method = "kmeans", # one of: "ward.D", "ward.D2", "single", "complete", "average", "mcquitty", "median", "centroid", "kmeans"
  index = "silhouette"
)
# -> takes a really long time and gives converge warning. 
nbclust_out
```

# K-means with K = 140
In the elbow plot I see wss going up a little bit again at a value of k at around 140. Therefore I decided to run kmeans with k = 140. But this is rather arbitrary.  

```{r}
# fit the k-means clustering with 119 clusters
k_means_fit119 <- kmeans(glove_embedding, 119, iter.max = 30, nstart = 25)

# look at the size of the clusters
k_means_fit119$size
min(k_means_fit119$size)
max(k_means_fit119$size)
# Examine clusters that have significantly fewer observations than other clusters. Clusters that have very few observations may contain outliers or unusual observations with unique characteristics. No clusters with extreme low number of observations. Minimum is 34 and maximum is 246

# The cost function in kmeans is the total sum of the squares
k_means_fit119$totss

# check results 
k_means_fit119
# -> 27.8% of the total variance in the data set that is explained by the clustering. 1% more than with 100 clusters

# Create data frame in which the merge cluster assignment back to rows/word. 
words_with_cluster119 <- as.data.frame(cbind(row.names(glove_embedding), k_means_fit119$cluster))

# add column names
names(words_with_cluster119) <- c("word", "kmeans119")

# save this data frame which contains a column with words and a column with to which cluster they belong
saveRDS(words_with_cluster119, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/clustering119.RData")

# check the largest cluster with 246 observations
cluster119_55 <- subset(words_with_cluster119, 
                   subset=kmeans119 == 55)
# -> cluster includes all sorts of abbreviations 

# check the smallest cluster with 34 observations
cluster119_32 <- subset(words_with_cluster119, 
                   subset=kmeans119 == 32)
# -> contains single letters and different units of measurement. 

# Health
# find out in which cluster the word health is assigned
words_with_cluster119[words_with_cluster119$word == "health", ]

# make a df of cluster 85
cluster119_85 <- subset(words_with_cluster119, 
                    subset=kmeans119 == 85)

# Depression
# find out in which cluster the word depression is assigned
words_with_cluster119[words_with_cluster119$word == "depression", ]

# make a df of cluster 10
cluster119_10 <- subset(words_with_cluster119, 
                    subset=kmeans119 == 10)
# -> this cluster also contains the word depressive but not the word depressed. 

words_with_cluster119[words_with_cluster119$word == "depressed", ]
words_with_cluster119[words_with_cluster119$word == "nondepressed", ]
words_with_cluster119[words_with_cluster119$word == "antidepressant", ]
```


# Try some other indices to determine K
```{r}
library(clusterCrit)
int_idx_75 <- intCriteria(glove_embedding, kmeans_fit75$cluster, c("Calinski_Harabasz", "Davies_Bouldin"))

int_idx_100 <- intCriteria(glove_embedding, kmeans_fit100$cluster, c("Calinski_Harabasz", "Davies_Bouldin"))

int_idx_125 <- intCriteria(glove_embedding, kmeans_fit125$cluster, c("Calinski_Harabasz", "Davies_Bouldin"))

int_idx_150 <- intCriteria(glove_embedding, kmeans_fit150$cluster, c("Calinski_Harabasz", "Davies_Bouldin"))
```

