---
title: "Try - out DBSCAN"
author: "Amy van der Ham"
date: "11/16/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load libraries
library(dplyr)
library(cluster)
library(ggplot2)
library(devtools)
library(data.table, quietly = TRUE, warn.conflicts = FALSE)

# libraries dbscan
library(fpc)
library(dbscan)
```

# set.seed prior to running the k-means clustering 
```{r}
set.seed(88)
```

# Load needed datafiles
```{r}
# load glove word embedding file
glove_embedding <- readRDS("glove_embedding.RData")

# check structure
str(glove_embedding)

# convert dataframe to a matrix
glove_embedding <- as.matrix(glove_embedding)
str(glove_embedding)
```

# Try - out dbscan tutorial 
http://www.sthda.com/english/wiki/wiki.php?id_contents=7940
```{r}
# Compute DBSCAN 
db <- dbscan::dbscan(glove_embedding, 8, 5) 
# Plot DBSCAN results
plot(db, glove_embedding, main = "DBSCAN", frame = FALSE)

# same plot using different function 
library("factoextra")
fviz_cluster(db, glove_embedding, stand = FALSE, frame = FALSE, geom = "point")

# Print DBSCAN results 
print(db)
# -> gives one big cluster and 402 noise points 

# cluster membership
db$cluster

# determining optimal eps value
dbscan::kNNdistplot(glove_embedding, k =  5)
abline(h = 0.15, lty = 2)


# try dbscan met eps = 4
db4 <- dbscan::dbscan(glove_embedding, 4, 5) 

# Print DBSCAN results 
print(db4)
# gives 17 clusters but many noise points (12557)

# try dbscan met een andere minPts value
db4_10 <- dbscan::dbscan(glove_embedding, 4, 10) 
print(db4_10)

# random attempt
db_ra <- dbscan::dbscan(glove_embedding, .25, 10) 
print(db_ra)


```
The method proposed here consists of computing the he k-nearest neighbor distances in a matrix of points.

The idea is to calculate, the average of the distances of every point to its k nearest neighbors. **The value of k will be specified by the user and corresponds to MinPts.**

Next, these k-distances are plotted in an ascending order. The aim is to determine the “knee”, which corresponds to the optimal eps parameter

