---
title: "Try - out DBSCAN"
author: "Amy van der Ham"
date: "11/16/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load libraries
library(dplyr)
library(cluster)
library(ggplot2)
library(devtools)
library(data.table, quietly = TRUE, warn.conflicts = FALSE)

# libraries dbscan
library(fpc)
library(dbscan)
```

# set.seed prior to running the k-means clustering 
```{r}
set.seed(88)
```

# Load needed datafiles
```{r}
# load glove word embedding file
glove_embedding <- readRDS("glove_embedding.RData")

# check structure
str(glove_embedding)
```

# Try - out dbscan tutorial 
http://www.sthda.com/english/wiki/wiki.php?id_contents=7940
```{r}
# Compute DBSCAN 
db <- dbscan::dbscan(glove_embedding, 8, 5) 
# Plot DBSCAN results
plot(db, glove_embedding, main = "DBSCAN", frame = FALSE)

# same plot using different function 
library("factoextra")
fviz_cluster(db, glove_embedding, stand = FALSE, frame = FALSE, geom = "point")

# Print DBSCAN results 
print(db)
# -> gives one big cluster and 402 noise points 

# cluster membership
db$cluster

# determine minPts 
library(SciViews)
# I have found online that you should set minPts to ln(n) so that is why this is calculated below. 
ln(12743)

# determining optimal eps value
dbscan::kNNdistplot(glove_embedding, k =  9)
abline(h = 7.9, lty = 2)
# -> based on this plot I would set eps to either 4.6 or 7.9 but not sure if I interpreted it correctly 

# based on the running the codelines above try dbscan with minPts = 9 and eps = 7.9
db_7.9_9 <- dbscan::dbscan(glove_embedding, 7.9, 9) 
print(db_7.9_9)

db_4.6_9 <- dbscan::dbscan(glove_embedding, 4.6, 9) 
print(db_4.6_9)

# Create data frame in which the cluster assignment is merged back to rows/word. 
kw_with_cluster <- as.data.frame(cbind(row.names(glove_embedding), db_4.6_9$cluster))
names(kw_with_cluster) <- c("word", "dbscan7")

cluster1 <- subset(kw_with_cluster, subset=dbscan7 == 1)
cluster2 <- subset(kw_with_cluster, subset=dbscan7 == 2)
cluster3 <- subset(kw_with_cluster, subset=dbscan7 == 3)
cluster4 <- subset(kw_with_cluster, subset=dbscan7 == 4)
cluster5 <- subset(kw_with_cluster, subset=dbscan7 == 5)
cluster6 <- subset(kw_with_cluster, subset=dbscan7 == 6)
cluster7 <- subset(kw_with_cluster, subset=dbscan7 == 7)

# I have also read somewhere that you should set minPts to 2*dim. Which in our case means 2*300 = 600. Let try what happens if we do that
# determining optimal eps value
dbscan::kNNdistplot(glove_embedding, k =  600)
abline(h = 6.5, lty = 2)
abline(h = 9.2, lty = 2)

# based on the running the codelines above try dbscan with minPts = 600 and eps = 6.5
db_6.5_600 <- dbscan::dbscan(glove_embedding, 6.5, 600) 
print(db_6.5_600)
# -> geeft 1 cluster en de rest als noise points. 

# TRYOUTS
# try dbscan met eps = 4 and minPts = 5
db4 <- dbscan::dbscan(glove_embedding, 4, 5) 

# Print DBSCAN results 
print(db4)
# gives 17 clusters but many noise points (12557)

# try dbscan met een andere minPts value
db4_10 <- dbscan::dbscan(glove_embedding, 4, 10) 
print(db4_10)

# random attempt
db_ra <- dbscan::dbscan(glove_embedding, .25, 10) 
print(db_ra)


# try dbscan with smaller eps. : eps = 0.10
db10_4 <- dbscan::dbscan(glove_embedding, 0.10, 4) 
print(db10_4)
# -> this small eps value will lead to all the point being noise

# try dbscan with lager eps. : eps = 0.35
db1.5_4 <- dbscan::dbscan(glove_embedding, 1.5, 10000) 
print(db1.5_4)
```
The method proposed here consists of computing the k-nearest neighbor distances in a matrix of points.

The idea is to calculate, the average of the distances of every point to its k nearest neighbors. **The value of k will be specified by the user and corresponds to MinPts.**

Next, these k-distances are plotted in an ascending order. The aim is to determine the “knee”, which corresponds to the optimal eps parameter

