---
title: "K-means Clustering results eindrapport"
author: "Amy van der Ham"
date: "12/23/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Try out k-means clustering on the existing GloVe embedding on which the final filter is applied.

```{r}
# load libraries
library(dplyr)
library(cluster)
library(ggplot2)
library(devtools)
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
library(factoextra)
```

# set.seed prior to running the k-means clustering 
DIT KAN HIER WEL WEG OMDAT IK HET DAARNA NOG MEERDERE MALEN RUN 
```{r}
set.seed(88)
```

## Load the embeddings 
```{r}
# load glove word embedding file
glove_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_final.RData")

str(glove_embedding)

# load glove bigrams word embedding file
glove_bigrams_embedding <-  readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_bigrams.RData")

str(glove_bigrams_embedding)

# load w2v word embedding file
w2v_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding.RData")

str(w2v_embedding)

# load w2v bigrams word embedding file
w2v_bigrams_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_bigrams_embedding.RData")

str(w2v_bigrams_embedding)

# Load ASReview embedding 
asr_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/asreview_embedding_sim.RData")

asr_embedding <- as.matrix(asr_embedding)

str(asr_embedding)

# -> Note that on this embedding the final filter has not yet been applied. 
```

# COSINE SIMILARITY
# Look at wich words are close to health
```{r}
library(text2vec)
# create function to find similar words based on cosine distance
find_similar_words <- function(word, embedding_matrix, n = 5) {
  similarities <- embedding_matrix[word, , drop = FALSE] %>%
    sim2(embedding_matrix, y = ., method = "cosine")
  
  similarities[, 1] %>% sort(decreasing = TRUE) %>% head(n)
}

# Run function on the word health and see the 25 closest words based on cosine similarity. Compare the different embeddings.
find_similar_words("white",glove_embedding,50)
find_similar_words("white",w2v_embedding,50)
find_similar_words("white",w2v_bigrams_embedding,50)
find_similar_words("mental_health",w2v_bigrams_embedding,50)

# check if socio-emotional and socioemotional are similar words in the glove bigrams embedding
find_similar_words("socio-emotional",glove_bigrams_embedding,25)
find_similar_words("socioemotional",glove_bigrams_embedding,25)


# check cosine similarity after applying filter on asr embedding 
# Load ASReview embedding 
asr_embedding_filter <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/asreview_embedding_sim.RData")

final_filter <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/final_filter.RData")

# create df in which only the words that we want to be included are kept
asr_embedding_filter <- subset(asr_embedding_filter,  rownames(asr_embedding_filter)%in% final_filter$filter_lemma)

asr_embedding_filter <- as.matrix(asr_embedding_filter)

# check cosine distance of asr embedding on which filter has been applied. 
find_similar_words("boy", asr_embedding_filter,10)
find_similar_words("emotion", asr_embedding_filter,15)
find_similar_words("boy", glove_embedding,15)
find_similar_words("boy", w2v_embedding,10)


```

# DETERMINING THE OPTIMAL NUMBER OF CLUSTER, K. 
Determining the value of the parameter K for the glove_embedding matrix. 
Function below is retrieved from the following page: https://www.r-bloggers.com/2013/08/k-means-clustering-from-r-in-action/ 
```{r}
wssplot <- function(data, nc=15, seed=88){
  wss <- (nrow(data)-1)*sum(apply(data,2,var))
  for (i in 2:nc){
    set.seed(seed)
    wss[i] <- sum(kmeans(data, centers=i, iter.max = 30)$withinss)}
  plot(1:nc, wss, type="b", xlab="Number of Clusters",
       ylab="Within groups sum of squares")}

wssplot(glove_embedding, nc=150)
```

# set seed again
```{r}
set.seed(88)
```

# Using the package factoextra
Examples on how to use this packages are retrieved from the following page: 
https://statsandr.com/blog/clustering-analysis-k-means-and-hierarchical-clustering-by-hand-and-in-r/#silhouette-method
```{r}
# Elbow method
set.seed(88)
elbow_plot_glove <- fviz_nbclust(glove_embedding, kmeans, iter.max = 40, nstart = 25, method = "wss", k.max = 150) +
  labs(subtitle = "Elbow method") # add subtitle

elbow_plot_glove +
      scale_x_discrete(breaks = levels(elbow_plot_glove$clusters)[c(T, rep(F, 9))]) # following line should make sure that on the axis the value is shown every 10 clusters but does not seem to be working. 

# Silhouette method
fviz_nbclust(glove_embedding, kmeans, iter.max = 30, nstart = 25, method = "silhouette", k.max = 150) +
  labs(subtitle = "Silhouette method")

# Takes to long so did not run this. Could turn nboot down. 
# Gap statistic
fviz_nbclust(glove_embedding, kmeans,
  iter.max = 30,
  nstart = 25,
  method = "gap_stat",
  nboot = 500 # reduce it for lower computation time (but less precise results)
) +
  labs(subtitle = "Gap statistic method")


# try to determine number of cluster with NbClust package
library(NbClust)
nbclust_out <- NbClust(
  data = glove_embedding,
  distance = "euclidean",
  min.nc = 2, # minimum number of clusters
  max.nc = 150, # maximum number of clusters
  method = "kmeans", # one of: "ward.D", "ward.D2", "single", "complete", "average", "mcquitty", "median", "centroid", "kmeans"
  index = "silhouette"
)
# -> takes a really long time and gives converge warning. 
nbclust_out

# Gap statistic
fviz_nbclust(glove_embedding, kmeans,
  iter.max = 30,
  nstart = 25,
  method = "gap_stat",
  nboot = 5 # reduce it for lower computation time (but less precise results)
) +
  labs(subtitle = "Gap statistic method")
```

# CLUSTERING ANALYSIS
Run kmeans with a value for k of 75, 100, 125, 150 and compare the results. For now I only did this on the glove embedding.
```{r}

# fit the k-means clustering with 75 clusters, glove
set.seed(88)
kmeans_fit75 <- kmeans(glove_embedding, 75, iter.max = 30, nstart = 25)


# fit the k-means clustering with 100 clusters
set.seed(88)
kmeans_fit100 <- kmeans(glove_embedding, 100, iter.max = 30, nstart = 25)

# fit the k-means clustering with 125 clusters
set.seed(88)
kmeans_fit125 <- kmeans(glove_embedding, 125, iter.max = 30, nstart = 25)


# fit the k-means clustering with 150 clusters
set.seed(88)
kmeans_fit150 <- kmeans(glove_embedding, 150, iter.max = 30, nstart = 25)
```

# RESULTS
Look at the fit of runnig kmeans on the glove embedding with k = 125 and compare these result with running kmeans on the word2vec embedding including bigrams with k = 125 . 
```{r}
# results 
kmeans_fit125

# obtain the centroids
kmeans_fit125$centers

# look at the size of the clusters
kmeans_fit125$size
min(kmeans_fit125$size)
max(kmeans_fit125$size)
# -> do not see a cluster with extremely low number of observations. Minimum is 36 and max is 289

# The cost function in kmeans is the total sum of the squares
kmeans_fit125$totss

# silhouette width
sil <- silhouette(kmeans_fit125$cluster, dist(glove_embedding))
fviz_silhouette(sil)
# -> the average silhouette width is low and there are quite some negative values. 
# lowsil: cluster 7, -.05, cluster 124, -04, cluster 87, -0.07. 
# highsil: cluster 123, 0.11, cluster 47, 0,13

# CHECK CLUSTERS
# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster125 <- as.data.frame(cbind(row.names(glove_embedding), kmeans_fit125$cluster))
# add column names
names(words_with_cluster125) <- c("word", "kmeans125")

# Check cluster with highest silhouette average
cluster125_hghsil <- subset(words_with_cluster125, subset=kmeans125 == 47)

# Check smallest cluster 
cluster125_97 <- subset(words_with_cluster125, subset=kmeans125 == 97)

# Mother
# find out in which cluster the word mother is assigned
words_with_cluster125[words_with_cluster125$word == "mother", ]

cluster125_80 <- subset(words_with_cluster125, subset=kmeans125 == 80)

# find out in which cluster the word ethnic is assigned
words_with_cluster125[words_with_cluster125$word == "ethnic", ]

cluster125_75 <- subset(words_with_cluster125, subset=kmeans125 == 75)

# find out to which cluster the word academic is assigned
words_with_cluster125[words_with_cluster125$word == "academic", ]

cluster125_17 <- subset(words_with_cluster125, subset=kmeans125 == 17)

# find out to which cluster the word yoga is assigned
words_with_cluster125[words_with_cluster125$word == "yoga", ]

cluster125_28 <- subset(words_with_cluster125, subset=kmeans125 == 28)

cluster125_21 <- subset(words_with_cluster125, subset=kmeans125 == 21)

# check a cluster with a low average silhouette width
cluster125_lowsil <- subset(words_with_cluster125, subset=kmeans125 == 27)

# check a cluster with a low average silhouette width
cluster125_lowsil2 <- subset(words_with_cluster125, subset=kmeans125 == 124)
# contains un and non words. 


# CLUSTER ANALYSIS WITHIN CLUSTER 
# create new subset data frame
embedding_cluster21 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_21$word)

# fit k-means
set.seed(88)
kmeans_fit3_cluster21 <- kmeans(embedding_cluster21, 3, iter.max = 30, nstart = 25)

# look at the results
# Create data frame in which the merge cluster assignment back to rows/word. 
words_with_cluster21_3 <- as.data.frame(cbind(row.names(embedding_cluster21), kmeans_fit3_cluster21$cluster))
# add column names
names(words_with_cluster21_3) <- c("word", "kmeans3")

# make a df for the 3 cluster results
cluster21_1 <- subset(words_with_cluster21_3, subset=kmeans3 == 1)
cluster21_2 <- subset(words_with_cluster21_3, subset=kmeans3 == 2)
cluster21_3 <- subset(words_with_cluster21_3, subset=kmeans3 == 3)

# set max overlap to Inf to show all the labels in the plot. This does however make the plot unreadable
#options(ggrepel.max.overlaps = Inf)

# visualize the k-means (with k = 3) clusters
fviz_cluster(kmeans_fit3_cluster21, data = embedding_cluster21,
palette = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07"),
ellipse.type = "euclid", # Concentration ellipse
star.plot = TRUE, # Add segments from centroids to items
repel = TRUE, # Avoid label overplotting (slow)
ggtheme = theme_minimal()
)

# CLUSTER ANALYSIS W2V BIGRAMS
set.seed(88)
# NOTE apparently forgot to run earlier on so the cluster assignments are not in line with the code below. -> should work now have adjusted code based on running this after running set.seed() above.  

# fit the k-means clustering with 125 clusters on w2v bigrams embedding.
kmeans_fit125_w2v <- kmeans(w2v_bigrams_embedding, 125, iter.max = 30, nstart = 25)

# Create data frame in which the cluster assignment is merged back to rows/word. 
words_with_cluster125_w2v <- as.data.frame(cbind(row.names(w2v_bigrams_embedding), kmeans_fit125_w2v$cluster))
# add column names
names(words_with_cluster125_w2v) <- c("word", "kmeans125")

# find out to which cluster the word emotional_dysregulation is assigned
words_with_cluster125_w2v[words_with_cluster125_w2v$word == "emotional_dysregulation", ]

cluster125_w2v_59 <- subset(words_with_cluster125_w2v, subset=kmeans125 == 59)

# find out to which cluster the word emotion is assigned
words_with_cluster125_w2v[words_with_cluster125_w2v$word == "emotion", ]

cluster125_w2v_25 <- subset(words_with_cluster125_w2v, subset=kmeans125 == 25)

# find out to which cluster the word family is assigned
words_with_cluster125_w2v[words_with_cluster125_w2v$word == "family", ]

cluster125_w2v_113 <- subset(words_with_cluster125_w2v, subset=kmeans125 == 113)

```


# VISUALIZE THE RESULTS
```{r}
# TSNE VISUALIZATION OF CLUSTER 97 (SMALLEST CLUSTER)
library(Rtsne)

# create plot of separate cluster with tsne
embedding_cluster97 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_97$word)

tsne_clst97 <- Rtsne(embedding_cluster97, dims = 2, perplexity = 10, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster97_plot <- as.data.frame(embedding_cluster97)

embedding_cluster97_plot$word <- rownames(embedding_cluster97_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst97 $Y) %>%
  mutate(
    word = embedding_cluster97_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 97") +
  theme(legend.position = "none") +
  theme_minimal()
p

# TSNE VISUALIZATION OF CLUSTER 80 (family related cluster)
# create plot of separate cluster with tsne
embedding_cluster80 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_80$word)

set.seed(88)
tsne_clst80 <- Rtsne(embedding_cluster80, dims = 2, perplexity = 25, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster80_plot <- as.data.frame(embedding_cluster80)

embedding_cluster80_plot$word <- rownames(embedding_cluster80_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst80 $Y) %>%
  mutate(
    word = embedding_cluster80_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 80") +
  theme(legend.position = "none") +
  theme_minimal()
p

# TSNE VISUALIZATION OF CLUSTER 75 (ethnicity related cluster)
# create plot of separate cluster with tsne
embedding_cluster75 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_75$word)

tsne_clst75 <- Rtsne(embedding_cluster75, dims = 2, perplexity = 20, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster75_plot <- as.data.frame(embedding_cluster75)

embedding_cluster75_plot$word <- rownames(embedding_cluster75_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst75 $Y) %>%
  mutate(
    word = embedding_cluster75_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 75") +
  theme(legend.position = "none") +
  theme_minimal() + 
  xlim(-15, 15)
p

# TSNE VISUALIZATION OF CLUSTER 17 (academic related cluster)
# create plot of separate cluster with tsne
embedding_cluster17 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_17$word)

tsne_clst17 <- Rtsne(embedding_cluster17, dims = 2, perplexity = 25, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster17_plot <- as.data.frame(embedding_cluster17)

embedding_cluster17_plot$word <- rownames(embedding_cluster17_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst17 $Y) %>%
  mutate(
    word = embedding_cluster17_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 17") +
  theme(legend.position = "none") +
  theme_minimal() +   
  xlim(-8, 8)
p


# TSNE VISUALIZATION OF CLUSTER low silhouette average (cluster 124 with non, un, post, pre)
# create plot of separate cluster with tsne
embedding_cluster124 <- subset(glove_embedding, rownames(glove_embedding) %in% cluster125_lowsil2$word)

tsne_clst124 <- Rtsne(embedding_cluster124, dims = 2, perplexity = 20, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster124_plot <- as.data.frame(embedding_cluster124)

embedding_cluster124_plot$word <- rownames(embedding_cluster124_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst124 $Y) %>%
  mutate(
    word = embedding_cluster124_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 124") +
  theme(legend.position = "none") +
  theme_minimal() +
    xlim(-13, 12)
p


## VISUALIZATION OF PLOTS FROM CLUSTERING WIHT W2V EMBEDDINGS ##
# TSNE VISUALIZATION OF CLUSTER 112 (emotional_dysregulation cluster)
# create plot of separate cluster with tsne
embedding_cluster59_w2v <- subset(w2v_bigrams_embedding, rownames(w2v_bigrams_embedding) %in% cluster125_w2v_59$word)

tsne_clst_59_w2v <- Rtsne(embedding_cluster59_w2v, dims = 2, perplexity = 95, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster59_w2v_plot <- as.data.frame(embedding_cluster59_w2v)

embedding_cluster59_w2v_plot$word <- rownames(embedding_cluster59_w2v_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst_59_w2v$Y) %>%
  mutate(
    word = embedding_cluster59_w2v_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word, colour = word == "emotional_dysregulation"), size = 3, show.legend = FALSE) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 59 - W2V") +
  scale_colour_manual(values=c("#000000", "#ffcc00")) +
  theme(legend.position = "none") +
  
  theme_minimal() 
p


# TSNE VISUALIZATION OF CLUSTER W2V 117 (family related cluster)
# note that for some reason the plots below do not show the bigrams. 
# create plot of separate cluster with tsne
embedding_cluster113_w2v <- subset(w2v_bigrams_embedding, rownames(w2v_bigrams_embedding) %in% cluster125_w2v_113$word)

tsne_clst_113_w2v <- Rtsne(embedding_cluster113_w2v, dims = 2, perplexity = 18, verbose=TRUE, max_iter = 500, pca = TRUE)

# create df that can be used for making the plot. 
embedding_cluster113_w2v_plot <- as.data.frame(embedding_cluster113_w2v)

embedding_cluster113_w2v_plot$word <- rownames(embedding_cluster113_w2v_plot)

# create plot
#colors = rainbow(length(unique(embedding_cluster91_plot$word)))
#names(colors) = unique(embedding_cluster91_plot$word)

plot_df <- data.frame(tsne_clst_113_w2v$Y) %>%
  mutate(
    word = embedding_cluster113_w2v_plot$word,
  ) 
p <- ggplot(plot_df, aes(X1, X2)) +
  geom_text(aes(X1, X2, label = word), size = 3) +
  xlab("") + ylab("") +
  ggtitle("2-dimensional t-SNE Mapping of Word Vectors Belonging to Cluster 113 - W2V") +
  theme(legend.position = "none") +
  theme_minimal() +
  xlim(-35, 38)
p
```


# INTERNAL VALIDATION
# Try some internal validation measures to evaluate the results.
```{r}
library(clusterCrit)

int_idx_75 <- intCriteria(glove_embedding, kmeans_fit75$cluster, c("Calinski_Harabasz", "Davies_Bouldin", "S_Dbw"))

int_idx_100 <- intCriteria(glove_embedding, kmeans_fit100$cluster, c("Calinski_Harabasz", "Davies_Bouldin", "S_Dbw"))

int_idx_125 <- intCriteria(glove_embedding, kmeans_fit125$cluster, c("Calinski_Harabasz", "Davies_Bouldin", "S_Dbw"))

int_idx_150 <- intCriteria(glove_embedding, kmeans_fit150$cluster, c("Calinski_Harabasz", "Davies_Bouldin", "S_Dbw"))

# NbClust can be used for determining the optimal number of clusters but this line of code takes a really long time to run. The NbClust also provides a function that also tells you which is the best clustering technique for your data but I was not able to figure out how to run and interpret that function properly.  
library(NbClust)
NbClust(glove_embedding, distance = "euclidean", method = "kmeans")

```

