---
title: "Save filter as .csv for use in Phyton"
author: "Amy van der Ham"
date: "12/06/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## RUN ONCE ##
save filters as .csv
```{r}
# load final filter 
final_filter <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/final_filter.RData")

# save as .csv
write.csv(final_filter,"/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/final_filter.csv", row.names = FALSE)

# load bigrams filter
bigrams_filter <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/bigrams_filter.RData")

# save as .csv
write.csv(bigrams_filter,"/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/bigrams_filter.csv", row.names = FALSE)
```

## RUN ONCE ##
clean and save w2v embeddings. 
```{r}
# load pretrained word2vec 
wrd2vec_embedding <- read.csv("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/pretrained_w2v_filtered.csv", header = FALSE)

# adjust the first column name to word
colnames(wrd2vec_embedding)[1] <- "word"

# check structure of dataframe
str(wrd2vec_embedding)

# remove certain characters from the column V2 which now is column of the type character and contains a string as value. 
library(tidyverse)
# create new data frame that can be used for applying adjustments
df_w2vemb <- wrd2vec_embedding

# remove the [ character from V2 
df_w2vemb$V2 <-gsub("\\[","",as.character(df_w2vemb$V2))

# remove the ] character from V2 
df_w2vemb$V2 <-gsub("\\]","",as.character(df_w2vemb$V2))

# remove the \n character from V2 
df_w2vemb$V2 <-gsub("\\\n","",as.character(df_w2vemb$V2))

# check if removing the characters went correctly 
df_w2vemb[1,c("word", "V2")]
# -> yes there are now only numbers (the vectors)

# split column V2 into multiple columns
library(splitstackshape)
# separate on the space
df_w2vemb <- cSplit(df_w2vemb, "V2", " ")

# retain dimensions of data frame
dim(df_w2vemb)
# -> we have 10077 words that are defined by 300 dimensions.

# check values after splitting
df_w2vemb[1,]
# -> looks the same as before 

# rename the column names of the data frame.
# First column is named word and the other columns dim1-40
colnames(df_w2vemb) <- c("word", paste0("dim", 1:300))

# save the embedding 
# convert the first column, word, to row index.
w2v_embedding <- df_w2vemb %>%
     remove_rownames() %>%
     column_to_rownames(var = 'word')

# convert dataframe to a matrix
w2v_embedding <- as.matrix(w2v_embedding)
str(w2v_embedding)

# save the cleaned w2v embedding 
saveRDS(w2v_embedding, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding2.RData")
```

## MOMENT OF TRUTH - CHECK IF CSV WITH CORRECT FINAL FILTER HAS BEEN PROPERLY SAVED
clean and save w2v embeddings. 
```{r}
# load pretrained word2vec 
wrd2vec_embedding <- read.csv("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/pretrained_w2v_filtered2.csv", header = FALSE)

# adjust the first column name to word
colnames(wrd2vec_embedding)[1] <- "word"

# check structure of dataframe
str(wrd2vec_embedding)

# remove certain characters from the column V2 which now is column of the type character and contains a string as value. 
library(tidyverse)
# create new data frame that can be used for applying adjustments
df_w2vemb <- wrd2vec_embedding

# remove the [ character from V2 
df_w2vemb$V2 <-gsub("\\[","",as.character(df_w2vemb$V2))

# remove the ] character from V2 
df_w2vemb$V2 <-gsub("\\]","",as.character(df_w2vemb$V2))

# remove the \n character from V2 
df_w2vemb$V2 <-gsub("\\\n","",as.character(df_w2vemb$V2))

# check if removing the characters went correctly 
df_w2vemb[1,c("word", "V2")]
# -> yes there are now only numbers (the vectors)

# split column V2 into multiple columns
library(splitstackshape)
# separate on the space
df_w2vemb <- cSplit(df_w2vemb, "V2", " ")

# retain dimensions of data frame
dim(df_w2vemb)
# -> we have 10077 words that are defined by 300 dimensions.

# check values after splitting
df_w2vemb[1,]
# -> looks the same as before 

# rename the column names of the data frame.
# First column is named word and the other columns dim1-40
colnames(df_w2vemb) <- c("word", paste0("dim", 1:300))

# save the embedding 
# convert the first column, word, to row index.
w2v_embedding <- df_w2vemb %>%
     remove_rownames() %>%
     column_to_rownames(var = 'word')

# convert dataframe to a matrix
w2v_embedding_finaloption <- as.matrix(w2v_embedding)
str(w2v_embedding)

# save the cleaned w2v embedding 
saveRDS(w2v_embedding_finaloption, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding_finaloption.RData")
```

The word2vec embedding including bigrams
```{r}
# load pretrained word2vec with bigrams included
w2v_embedding_bigram <- read.csv("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/pretrained_w2v_filtered_bigrams.csv", header = FALSE)

# adjust the first column name to word
colnames(w2v_embedding_bigram)[1] <- "word"

# check structure of dataframe
str(w2v_embedding_bigram)

# remove certain characters from the column V2 which now is column of the type character and contains a string as value. 
# create new data frame that can be used for applying adjustments
df_bigrams <- w2v_embedding_bigram

# remove the [ character from V2 
df_bigrams$V2 <-gsub("\\[","",as.character(df_bigrams$V2))

# remove the ] character from V2 
df_bigrams$V2 <-gsub("\\]","",as.character(df_bigrams$V2))

# remove the \n character from V2 
df_bigrams$V2 <-gsub("\\\n","",as.character(df_bigrams$V2))

# check if removing the characters went correctly 
df_bigrams[1,c("word", "V2")]
# -> yes there are now only numbers (the vectors)

# split column V2 into multiple columns
# separate on the space
df_bigrams <- cSplit(df_bigrams, "V2", " ")

# retain dimensions of data frame
dim(df_bigrams)
# -> we have 10297 words that are defined by 300 dimensions.

# check values after splitting
df_bigrams[1,]
# -> looks the same as before 

# rename the column names of the data frame.
# First column is named word and the other columns dim1-40
colnames(df_bigrams) <- c("word", paste0("dim", 1:300))

# save the embedding 
# convert the first column, word, to row index.
w2v_bigrams_embedding <- df_bigrams %>%
     remove_rownames() %>%
     column_to_rownames(var = 'word')

# convert dataframe to a matrix
w2v_bigrams_embedding <- as.matrix(w2v_bigrams_embedding)
str(w2v_bigrams_embedding)

# save the w2v embedding that includes bigrams 
saveRDS(w2v_bigrams_embedding, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_bigrams_embedding.RData")
```

## RUN ONCE ##
apply final filter on glove embedding and save. 
```{r}
# load glove vectors into R
vectors_glove <- data.table::fread('glove.840B.300d.txt', data.table = F,  encoding = 'UTF-8', quote="") 

# rename the columns
colnames(vectors_glove) <- c('word',paste('dim',1:300,sep = '_'))

# create df in which only the words that we want to be included are kept
filtered_embedding <- subset(vectors_glove, word %in% final_filter$filter_lemma)

# Make final GloVE embedding ready for analysis
# convert the first column, word, to row index.
glove_embedding <- filtered_embedding %>%
     remove_rownames() %>%
     column_to_rownames(var = 'word')

# convert dataframe to a matrix
glove_embedding <- as.matrix(glove_embedding)
str(glove_embedding)

# save the glove embedding to which the filter is applied so this can be easily loaded into other scripts
saveRDS(glove_embedding, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_final.RData")
```

Apply bigrams filter on glove embedding and save the embedding. 
```{r}
# CREATE GLOVE EMBEDDING WITH BIGRAMS
# load data frame with column with selection of words to include in analysis. 
df_bigrams_glove <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/bigrams_filter_glove.RData")

# create df in which only the words that we want to be included are kept
glove_embedding_bigrams <- subset(vectors_glove, word %in% df_bigrams_glove$filter_bigrams_glove)

# transform so that it can be saved
glove_emb_bigrams <- glove_embedding_bigrams %>%
     remove_rownames() %>%
     column_to_rownames(var = 'word')

# convert dataframe to a matrix
glove_emb_bigrams <- as.matrix(glove_emb_bigrams)
str(glove_emb_bigrams)

saveRDS(glove_emb_bigrams, "/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/try_outs/glove_embedding_bigrams.RData")
```


## START HERE ##
First load all the embeddings 
```{r}
# Load all the embeddings
# glove embedding 
glove_embedding <-  readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/glove_embedding_final.RData")

# glove embedding including bigrams
glove_bigrams_embedding <-  readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/glove_embedding_bigrams.RData")

# w2v embedding 
w2v_embedding_loaded <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding.RData")

w2v_embedding_newsaved <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding2.RData")

w2v_embedding_created <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_embedding2.RData")

# w2v embedding including bigrams
w2v_bigrams_embedding <- readRDS("/Users/amyvanderham/Documents/Research_Assistant_Rgit/veni_sysrev/amy/w2v_bigrams_embedding.RData")

```

# Check for each embedding which words are lost 
Note that filters, final_filter, bigrams_filter and df_bigrams_glove need to be loaded in the pieces of code above before we can run the code below. 
```{r}
# GLOVE EMBEDDING 
# check number of unique words
length(unique((rownames(glove_embedding))))
# 11,562 unique words

# non-GloVe: check which words are in the final filter but are not in the glove embedding data and are therefore lost (unwanted).
lost_glove <- subset(final_filter, !(filter_lemma %in% rownames(glove_embedding)))
# 2,185 words lost  (had hier eerder 2,182 staan maar het lijkt erop dat dit een typo was)

length(unique(rownames(glove_embedding))) + length(unique((lost_glove$filter_lemma)))
# -> 13,747. Which is equal to the line of code below. 
length(unique((final_filter$filter_lemma)))

# GLOVE EMBEDDING INCLUDING BIGRAMS
# check number of unique words
length(unique((rownames(glove_bigrams_embedding))))
# 11,943 unique words

# non-GloVe: check which words are in the bigrams glove filter but are not in the glove embedding data and are therefore lost (unwanted).
lost_glove_bigrams <- subset(df_bigrams_glove, !(filter_bigrams_glove %in% rownames(glove_bigrams_embedding)))
# 17,175 words lost  

length(unique(rownames(glove_bigrams_embedding))) + length(unique((lost_glove_bigrams$filter_bigrams_glove)))
# -> 29,118. Which is equal to the line of code below. 
length(unique((bigrams_filter$filter_bigrams)))

# WORD2VEC EMBEDDING
# check number of unique words
length(unique((rownames(w2v_embedding))))
# 10,077 unique words

# non-w2v: check which words are in the final filter but are not in the w2v embedding data and are therefore lost (unwanted).
lost_w2v <- subset(final_filter, !(filter_lemma %in% rownames(w2v_embedding)))
# 3,670 words lost  

length(unique(rownames(w2v_embedding))) + length(unique((lost_w2v$filter_lemma)))
# -> 13,747. Which is equal to the line of code below. 
length(unique((final_filter$filter_lemma)))

# WORD2VEC EMBEDDING INCLUDING BIGRAMS
# check number of unique words
length(unique((rownames(w2v_bigrams_embedding))))
# 10,297 unique words

# non-w2v: check which words are in the bigrams filter but are not in the w2v embedding data and are therefore lost (unwanted).
lost_w2v_bigrams <- subset(bigrams_filter, !(filter_bigrams %in% rownames(w2v_bigrams_embedding)))
# 18,821 words lost  

length(unique(rownames(w2v_bigrams_embedding))) + length(unique((lost_w2v_bigrams$filter_bigrams)))
# -> 29,118. Which is equal to the line of code below. 
length(unique((bigrams_filter$filter_bigrams)))
```

# Comparison of the different embeddings 
```{r}
# COMPARE GLOVE AND GLOVE BIGRAMS
diff_glove <- subset(glove_bigrams_embedding, !(rownames(glove_bigrams_embedding) %in% rownames(glove_embedding)))
# -> if we look at the rownames this matrix we see that difference between the two matrices are indeed all bigrams. This isto be expected. 

# check the length of difference 
length(unique(rownames(diff_glove)))
length(unique(rownames(glove_bigrams_embedding))) - length(unique(rownames(glove_embedding))) 

# COMPARE W2V AND W2V BIGRAMS
diff_w2v <- subset(w2v_bigrams_embedding, !(rownames(w2v_bigrams_embedding) %in% rownames(w2v_embedding)))
# -> if we look at the rownames this matrix we see that difference between the two matrices are indeed all bigrams. This isto be expected. 
# check words that are in the glove embedding that are also in the w2v embedding

# check the length of difference 
length(unique(rownames(diff_w2v)))
length(unique(rownames(w2v_bigrams_embedding))) - length(unique(rownames(w2v_embedding))) 

# COMPARE GLOVE AND W2V
# check words that are in the glove embedding that are also in the w2v embedding
words_same <- subset(glove_embedding, rownames(glove_embedding) %in% rownames(w2v_embedding))

length(unique(rownames(words_same)))

# check words that are in the glove embedding but not in the w2v embedding 
words_diff <- subset(glove_embedding, !(rownames(glove_embedding) %in% rownames(w2v_embedding)))

length(unique(rownames(words_diff)))

length(unique(rownames(words_same))) + length(unique(rownames(words_diff))) == length(unique(rownames(glove_embedding)))

length(unique(rownames(w2v_embedding))) + length(unique(rownames(words_diff))) == length(unique(rownames(glove_embedding)))

# check words that are in the w2v embedding but not in the glove embedding 
words_diff_w2v <- subset(w2v_embedding, !(rownames(w2v_embedding) %in% rownames(glove_embedding)))

length(unique(rownames(w2v_embedding))) + length(unique(rownames(words_diff))) -  length(unique(rownames(words_diff_w2v))) == length(unique(rownames(glove_embedding)))

# COMPARE GLOVE BIGRAMS AND W2V BIGRAMS
# note that I will use diff_glove and diff_w2v here because the diff represent the bigrams that are included extracted from both different datasets, glove and w2v. 
# because the bigrams are split differently in the two dataset we first have to apply some data manipulations 
diff_glove_bigram_comp <- as.data.frame(diff_glove)
diff_glove_bigram_comp$word <- rownames(diff_glove_bigram_comp)
diff_glove_bigram_comp <- diff_glove_bigram_comp["word"]

# create column in which the bigrams part of the glove embedding are split with _ and not -. 
diff_glove_bigram_comp$w2v_style <- gsub('-', '_', diff_glove_bigram_comp$word)

# now check which bigrams are in the w2v embedding but not in the glove embedding
bigrams_in_w2v <- subset(diff_w2v, !(rownames(diff_w2v) %in% diff_glove_bigram_comp$w2v_style))

# Check which bigrams are in the glove embedding but not in the w2v embedding
bigrams_in_glove <- subset(diff_glove_bigram_comp, !(w2v_style %in% rownames(diff_w2v)))

# check which, and how many, bigrams are in both embeddings 
bigrams_both <- subset(diff_w2v, rownames(diff_w2v) %in% diff_glove_bigram_comp$w2v_style)
length(unique(rownames(bigrams_both)))
# -> interestingly the are only 45 bigrams that are in both embeddings. 

# check if things add up for w2v
length(unique(rownames(diff_w2v))) == length(unique(rownames(bigrams_both))) + length(unique(rownames(bigrams_in_w2v)))

# check if things add up for glove
length(unique(rownames(diff_glove))) == length(unique(rownames(bigrams_both))) + length(unique(rownames(bigrams_in_glove)))
```

